Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-10 papers/integration/omm_integ.tex
Adds start of section describing weight maps

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
described earlier) are shown in Fig.~\ref{weightmaps}.
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

>>>>

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
described earlier) are shown in Fig.~\ref{weightmaps}.

\rvw{Fig.~\ref{weightmaps}(a) shows the weight map for the muscle
which rotates the eye to the left. As we modelled a left eye, this
actuates the lateral rectus muscle. The exponential rise is seen in
the $r$ direction; as $r$ increases, so the connection strength to the
SBG channel rises exponentially. The connection strength is greatest
along the centre line, for a value of $\phi$ which corresponds to a
purely leftward movement. Note that $\phi$ is presented in neural
coordinates, and not in degrees or radians. $\phi=$37.5 corresponds
to movements left. In regions of the map for which there is no
leftward movement, that is, in the half of the map which corresponds
to any movement with a rightward component, the `left' weight map is
0. Fig.~\ref{weightmaps}(d) shows the weight map for rightward
movements, actuating the medial rectus muscle of the eye. The map is a
mirror of Fig.~\ref{weightmaps}(a), reflected about the line
$phi$=25. ETC ETC for DOWN UP and Z+, Z-.}
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);
